Time series clusters

### 2020-07-13 src/Data_Spatial.Rmd
I applied the new dates and estimated the clusters. leaflet map is the same. No more time to work on this this morning. I will try again tonight for the legends.

---
title: "Data_Spatial"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: html_document
df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

>>>>

---
title: "Data_Spatial"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

### 2020-07-13 src/ts_clusters.Rmd
I applied the new dates and estimated the clusters. leaflet map is the same. No more time to work on this this morning. I will try again tonight for the legends.

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2020, month = 2, day = 3),
                make_datetime(year = 2020, month = 2, day = 4),
                make_datetime(year = 2020, month = 2, day = 5),
                make_datetime(year = 2020, month = 2, day = 6),
                make_datetime(year = 2020, month = 2, day = 7)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide <- merge(ts.up2020, help.dates, by = "weekday")
ts.wide$hour <- paste(ts.wide$hour, ":00", sep="")
ts.wide$help.date.time <- with(ts.wide, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

@@

# impute with means of each TS
# TODO check sensitivity
library(imputeTS)
ts.wide <- na_mean(ts.wide)
#sapply(ts.wide, function(x) sum(is.na(x)))

@@

# impute with means of each TS
# TODO check sensitivity
library(imputeTS)
ts.wide <- na_mean(ts.wide)

@@

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2019, month = 2, day = 4),
                make_datetime(year = 2019, month = 2, day = 5),
                make_datetime(year = 2019, month = 2, day = 6),
                make_datetime(year = 2019, month = 2, day = 7),
                make_datetime(year = 2019, month = 2, day = 8)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide2019 <- merge(ts.up2019, help.dates, by = "weekday")
ts.wide2019$hour <- paste(ts.wide2019$hour, ":00", sep="")
ts.wide2019$help.date.time <- with(ts.wide2019, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

@@

# impute with means of each TS
# TODO check sensitivity
library(imputeTS)
ts.wide2019 <- na_mean(ts.wide2019)
#sapply(ts.wide, function(x) sum(is.na(x)))

@@

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2020, month = 2, day = 3),
                make_datetime(year = 2020, month = 2, day = 4),
                make_datetime(year = 2020, month = 2, day = 5),
                make_datetime(year = 2020, month = 2, day = 6),
                make_datetime(year = 2020, month = 2, day = 7)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide <- merge(ts.down2020, help.dates, by = "weekday")
ts.wide$hour <- paste(ts.wide$hour, ":00", sep="")
ts.wide$help.date.time <- with(ts.wide, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

@@

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2019, month = 2, day = 4),
                make_datetime(year = 2019, month = 2, day = 5),
                make_datetime(year = 2019, month = 2, day = 6),
                make_datetime(year = 2019, month = 2, day = 7),
                make_datetime(year = 2019, month = 2, day = 8)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide2019 <- merge(ts.down2019, help.dates, by = "weekday")
ts.wide2019$hour <- paste(ts.wide2019$hour, ":00", sep="")
ts.wide2019$help.date.time <- with(ts.wide2019, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

>>>>

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2020, month = 3, day = 2),
                make_datetime(year = 2020, month = 3, day = 3),
                make_datetime(year = 2020, month = 3, day = 4),
                make_datetime(year = 2020, month = 3, day = 5),
                make_datetime(year = 2020, month = 3, day = 6)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide <- merge(ts.up2020, help.dates, by = "weekday")
ts.wide$hour <- paste(ts.wide$hour, ":00", sep="")
ts.wide$help.date.time <- with(ts.wide, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

@@

# impute with means of each TS
# TODO check sensitivity
ts.wide <- na_mean(ts.wide)
#sapply(ts.wide, function(x) sum(is.na(x)))

@@

# impute with means of each TS
# TODO check sensitivity
ts.wide <- na_mean(ts.wide)

@@

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2019, month = 3, day = 4),
                make_datetime(year = 2019, month = 3, day = 5),
                make_datetime(year = 2019, month = 3, day = 6),
                make_datetime(year = 2019, month = 3, day = 7),
                make_datetime(year = 2019, month = 3, day = 8)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide2019 <- merge(ts.up2019, help.dates, by = "weekday")
ts.wide2019$hour <- paste(ts.wide2019$hour, ":00", sep="")
ts.wide2019$help.date.time <- with(ts.wide2019, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

@@

# impute with means of each TS
# TODO check sensitivity
ts.wide2019 <- na_mean(ts.wide2019)
#sapply(ts.wide, function(x) sum(is.na(x)))

@@

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2020, month = 3, day = 2),
                make_datetime(year = 2020, month = 3, day = 3),
                make_datetime(year = 2020, month = 3, day = 4),
                make_datetime(year = 2020, month = 3, day = 5),
                make_datetime(year = 2020, month = 3, day = 6)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide <- merge(ts.down2020, help.dates, by = "weekday")
ts.wide$hour <- paste(ts.wide$hour, ":00", sep="")
ts.wide$help.date.time <- with(ts.wide, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

@@

# create a 'fake' week for a ts id
help.dates <- tibble(help.date.time = c(make_datetime(year = 2019, month = 3, day = 4),
                make_datetime(year = 2019, month = 3, day = 5),
                make_datetime(year = 2019, month = 3, day = 6),
                make_datetime(year = 2019, month = 3, day = 7),
                make_datetime(year = 2019, month = 3, day = 8)),
                weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
ts.wide2019 <- merge(ts.down2019, help.dates, by = "weekday")
ts.wide2019$hour <- paste(ts.wide2019$hour, ":00", sep="")
ts.wide2019$help.date.time <- with(ts.wide2019, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
